Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-21 paper/paper.tex
related works

\subsubsection{Comparison with other tools}
 \Gui{There are a few reasons that makes the comparison between Syrius and other tools \Fix{impossible}

@@

\textbf{'content' option support.} Another limitation is the support of 'content' option. Most papers do not support rule generation with the 'content' option, using only classic DDoS attacks in the rule generation, like ICMP and SYN flood, which only use numerical and categorical options. Some papers do support 'content', but don't explain well how they handle those rules with exclusive 'content'.\Fix{citation needed}}
 \Luc{Vollmer \cite{vollmer-etal-cics2011} and Guruprasad \cite{guruprasad} used 
 evolutionaries approaches to 
autonomously generate rules using the Snort IDS. They built 
their own ICMP datasets by using packet creation tools or by capturing network traffic. 
Guruprasad also used DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets 
for non-ICMP attacks.

Vollmer created ten different packets to match ten existing rules, and then used 
these packets as input to the rule generation process. As a result, the produced 
rules achieved a 100\% detection rate and produced 3 false positives out of 33k packets.

Guruprasad manually created a set of rules by analyzing the network patterns and 
the datasets, this set of rules was used as the initial population of the algorithm. 
The produced rules achieved a detection rate up to 96\%, the false positive rate 
was not evaluated.

On our experiments with Syrius, we used a total of \totalPackets packets that 
matches \totalAttacks different existing rules and it was able to generate rules that detected 
all the packets with no false positives.  
 }  
\subsubsection{Running time}\Mar{}

@@

\noindent
\textbf{Alternative methods for rule synthesis.} We discuss in the
following techniques similar in goal to ours. Unfortunately, we could
not access the tools implementing the techniques for side
comparison. Nevertheless, we found that there are important
differences between our work and related work. Vollmer
\etal{}~\cite{vollmer-etal-cics2011} propose the use of search to
derive rules for Snort, which are very similar to \suri's.  Their
approach focuses on icmp attacks. It models every field of the icmp
packet in the chromosome of candidate solutions (\ie{}, a rule) of a
genetic search. The initial population is a set of candidate solutions
that randomly combine options, modelling the packet fields. They show
that they were able to generate rules without false negatives and only
3 false positives across 33K benign packets. The key differences
between our work and Vollmer~\etal{}'s are 1) the support of different
protocols and 2) the use of ranking to discriminate alternative
plausible rules. As for 1, our approach supports a variety of
protocols and options that refer to message payloads which
significantly increase the search space. The icmp rules they generate only
refer to message fields (see Section~\ref{sec:rules-and-packets}).
\MyComment{\Luc{eh possivel incluir contents em regras icmp tb. o q a secao 2.3 
diz q \textbf{geralmente} as regras nao-http possuem apenas field options}. }
As for 2, our solution additionally ranks plausible options, which
contain \emph{no} false positives or negatives with respect to the
benign and mallicious traffic considered. Muthuregunathan
\etal{}~\cite{muthuregunathan-etal2009} propose a clustering method to
create rules. They characterize candidate solutions as a set of field
values and use a clustering algorithm---hybrid k-means partitioned
around menoids---to isolate malicious from benign
traffic. Subsequently, they optimize the formed clusters using genetic
algorithms and hill-climbing search. Ou approach differs from theirs
in the method used, results, and support for content
options. Kao~\etal~\cite{Kao2015AutomaticNR} proposed ARGS, a system
to synthesize http rules that take malicious traffic as input. ARGS
looks for a common pattern across the different inputs to define
rules. It does not take existing rules as input or benign
traffic. Consequently, false positive can be produced and need to be
handled manually by users. Our approach, in contrast, does not
generate false positives w.r.t. the input traffic.

>>>>

\subsubsection{\Fix{Lack of }Comparison with other tools}
 \Gui{There are a few reasons that makes the comparison between Syrius and other tools \Fix{impossible}

@@

\textbf{'content' option support.} Another limitation is the support of 'content' option. Most papers do not support rule generation with the 'content' option, using only classic DDoS attacks in the rule generation, like ICMP and SYN flood, which only use numerical and categorical options. Some papers do support 'content', but don't explain well how they handle those rules with exclusive 'content'.\Fix{citation needed}}
%%  \Luc{Vollmer \cite{vollmer-etal-cics2011} and Guruprasad \cite{guruprasad} used 
%%  evolutionaries approaches to 
%% autonomously generate rules using the Snort IDS. They built 
%% their own ICMP datasets by using packet creation tools or by capturing network traffic. 
%% Guruprasad also used DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets 
%% for non-ICMP attacks.
%% 
%% Vollmer created ten different packets to match ten existing rules, and then used 
%% these packets as input to the rule generation process. As a result, the produced 
%% rules achieved a 100\% detection rate and produced 3 false positives out of 33k packets.
%% 
%% Guruprasad manually created a set of rules by analyzing the network patterns and 
%% the datasets, this set of rules was used as the initial population of the algorithm. 
%% The produced rules achieved a detection rate up to 96\%, the false positive rate 
%% was not evaluated. 
%% 
%% On our experiments with Syrius, we used a total of \totalPackets packets that 
%% matches \totalAttacks different existing rules and it was able to generate rules that detected 
%% all the packets with no false positives.  
%%  }  
\subsubsection{Running time}\Mar{}

@@

\noindent
\textbf{Alternative methods for rule synthesis.} We discuss in the
following techniques similar in goal to ours. Unfortunately, we could
not access the tools implementing the techniques for side
comparison. Nevertheless, we found that there are important
differences between our work and related work. Vollmer
\etal{}~\cite{vollmer-etal-cics2011} propose the use of search to
derive rules for Snort, which are very similar to \suri's.  Their
approach focuses on icmp attacks \Gui{, creating their own packets manually}. It models every field of the icmp
packet in the chromosome of candidate solutions (\ie{}, a rule) of a
genetic search. The initial population is a set of candidate solutions
that randomly combine options, modelling the packet fields. They show
that they were able to generate rules without false negatives and only
3 false positives across 33K benign packets. The key differences
between our work and Vollmer~\etal{}'s are 1) the support of different
protocols and 2) the use of ranking to discriminate alternative
plausible rules. As for 1, our approach supports a variety of
protocols and options that refer to message payloads which
significantly increase the search space. The icmp rules they generate only
refer to message fields (see Section~\ref{sec:rules-and-packets}).
\MyComment{\Luc{eh possivel incluir contents em regras icmp tb. o q a secao 2.3 
diz q \textbf{geralmente} as regras nao-http possuem apenas field options}. }
As for 2, our solution additionally ranks plausible options, which
contain \emph{no} false positives or negatives with respect to the
benign and mallicious traffic considered.\Gui{Guruprasad \cite{guruprasad} also proposes an evolutionary framework, creating their own ICMP dataset as Vollmer, but also using DARPA 1999 \cite{darpa1999} and ISCX 2012 \cite{iscx} datasets for non-ICMP attacks. The produced rules reported a detection rate up to 96\%. Although Guruprasad supports more protocols than Vollmer, our approach still supports more options and protocols, making both key differences considered when comparing with Vollmer also relevant with Guruprasad.} Muthuregunathan
\etal{}~\cite{muthuregunathan-etal2009} propose a clustering method to
create rules. They characterize candidate solutions as a set of field
values and use a clustering algorithm---hybrid k-means partitioned
around menoids---to isolate malicious from benign
traffic. Subsequently, they optimize the formed clusters using genetic
algorithms and hill-climbing search. Ou approach differs from theirs
in the method used, results, and support for content
options. Kao~\etal~\cite{Kao2015AutomaticNR} proposed ARGS, a system
to synthesize http rules that take malicious traffic as input. ARGS
looks for a common pattern across the different inputs to define
rules. It does not take existing rules as input or benign
traffic. Consequently, false positive can be produced and need to be
handled manually by users. Our approach, in contrast, does not
generate false positives w.r.t. the input traffic.
